---
title: "README"
author: "Yu-Heng Luo"
date: "2022-11-02"
output:
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# EnImpute2

README file for R package supporting the paper **"EnImpute2:A shiny
interface for implementing an effective ensemble imputation method for
dropout events"**.

# Contents of this archive

(1) pkg: subdirectory that contains the R package.
(2) shiny: subdirectory that contains the Shiny application.
(3) EnImpute2-manual.pdf: reference manual.

The EnImpute2 package has the following R-package dependencies:
DrImpute, Rmagic, rsvd, SAVER, scImpute,
scRMD,WGCNA,scNPF,SCRABBLE,scTSSR,scTSSR2,SDImpute,VIPER and zinbwave.
The dependencies will be automatically installed along with EnImpute2.
If the dependencies are not installed correctly, please install them by
yourself. You can install the dependencies using the following commands:

## DrImpute

```{r eval=FALSE}
install.packages("DrImpute")
```

## Rmagic

```{r eval=FALSE}
install.packages("Rmagic")
```

## rsvd

```{r eval=FALSE}
install.packages("rsvd")
```

## SAVER

```{r eval=FALSE}
library(devtools) 
devtools::install_github("mohuangx/SAVER")
```

## scImpute

```{r eval=FALSE}
library(devtools) 
install_github("Vivianstats/scImpute")
```

## scRMD

```{r eval=FALSE}
library(devtools) 
devtools::install_github("ChongC1990/scRMD")
```

## WGCNA

```{r eval=FALSE}
install.packages("WGCNA")
```

or

```{r eval=FALSE}
install.packages("BiocManager") 
BiocManager::install("WGCNA")
```

or

```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("cran/WGCNA")
```

## scNPF

```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("BMILAB/scNPF")
library(scNPF)
```

## SCRABBLE

```{r eval=FALSE}
install.packages("SCRABBLE")
```

## scTSSR

```{r eval=FALSE}
install.packages("devtools")
library("devtools")
install_github("Zhangxf-ccnu/scTSSR")
```

## scTSSR2

```{r eval=FALSE}
install.packages("devtools")
library("devtools")
install_github("Zhangxf-ccnu/scTSSR2")
```

## SDImpute

```{r eval=FALSE}
install.packages("devtools")         
library(devtools)           
install_github("Jinsl-lab/SDImpute")
```

## VIPER

```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("ChenMengjie/VIPER")
```

## zinbwave

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("drisso/zinbwave")
```

## bcp

```{r eval=FALSE}
install.packages("bcp")
```

EnImpute2 also depends on the following two Python packages: dca
(<https://github.com/theislab/dca>),MAGIC
(<https://github.com/KrishnaswamyLab/MAGIC>). Before installing
EnImpute2, please install the two Python packages following the
corresponding readme files, and check whether they can be run from the
command line.

You can use the following commands to install EnImpute2 from GitHub.

# Step 1. Install the devtools package. Invoke R and then type

install.packages("devtools")

# Step 2. Load the devtools package.

library("devtools")

# Step 3. Install the EnImpute package from GitHub.

install_github("leoluo12138/EnImpute2", subdir="pkg")

# Quick Start

To perform imputation, simply run:

```{r eval=FALSE}
library("EnImpute2")
data("baron")
baron_imputation_result = EnImpute2(baron$count.samp)
```

<!-- For detialed usages, please refer to "EnImpute2-manual.pdf". For more -->

<!-- examples about real data applications, please refer to the file -->

<!-- "down_sampling_analysis.R", which performs the down-sampling experiments -->

<!-- in the papar in the subdirectory "down_sampling_experiments". -->

Please do not hesitate to contact Yu-Heng Luo at
[luoyuheng\@mails.ccnu.edu.cn](mailto:luoyuheng@mails.ccnu.edu.cn){.email}
to seek any clarifications regarding any contents or operation of the
archive.
